False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2016-03-04 document/ms.tex
reorganization; readme updates

\slugcomment{}

@@

As there is significant interest in identifying potentially habitable
planets, \tab{hz} lists the properties of \nhz\ CANDIDATE KOIs newly
validated by this work that \textit{may} fall within the optimistic
habitable zones of their host stars \citep{Kopparapu:2013}, 
according to the stellar
properties reported by the DR24 table at the NExScI Archive.  We note
that while more detailed follow-up observations (imaging and
spectroscopy) have been taken for each of these targets, we make no
attempt here to characterize these systems in detail.  Analysis of
high-resolution spectroscopy in particular will solidify the
properties of these host stars, which will affect the habitable zone
boundaries.  We thus emphasize that this list is neither complete nor
final, serving only to draw attention to new validations of 
interest rather than to be a definitive statement on potential 
habitability.  We also note that based solely on the properties in the 
DR24 table, KOI-5475.01 (listed as having a 448-day orbital period) 
should also be included in this list of potentially habitable-zone
planets.  However, as explained in \citet[][Section 5.5.4]{Coughlin:2015},
this particular KOI actually has a 224-day period, making its insolation
to high to be within the habitable zone; we have thus excluded it 
from \tab{hz}.

>>>>

\slugcomment{note: this work is UNDER EMBARGO until publicly announced.}

@@

As there is significant interest in identifying potentially habitable
planets, \tab{hz} lists the properties of \nhz\ CANDIDATE KOIs newly
validated by this work that \textit{may} fall within the optimistic
habitable zones of their host stars \citep{Kopparapu:2013}, 
according to the stellar
properties reported by the DR24 table at the NExScI Archive.  We note
that while more detailed follow-up observations (imaging and
spectroscopy) have been taken for each of these targets, we make no
attempt here to characterize these systems in detail.  Analysis of
high-resolution spectroscopy in particular will solidify the
properties of these host stars, which will affect the habitable zone
boundaries.  We thus emphasize that this list is neither complete nor
final, serving only to draw attention to new validations of 
interest rather than to be a definitive statement on potential 
habitability.  We also note that based solely on the properties in the 
DR24 table, KOI-5475.01 (listed as having a 448-day orbital period) 
should also be included in this list of potentially habitable-zone
planets.  However, as explained in \citet[][Section 5.5.4]{Coughlin:2015},
this particular KOI actually has a 224-day period, making its insolation
too high to be within the habitable zone; we have thus excluded it 
from \tab{hz}.
